---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 144
)
```

# ggconsulting

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/viniciusoike/ggconsulting/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/viniciusoike/ggconsulting/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/viniciusoike/ggconsulting/graph/badge.svg)](https://app.codecov.io/gh/viniciusoike/ggconsulting)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

An opinionated ggplot2 extension for executive-grade consulting output. Ships three archetype themes, eleven palettes, locale-aware label helpers (pt-BR + en-US), and a data-aware polish layer.

> **Heads up:** ggconsulting is in early development. The public API is being shaped against real consulting decks; expect breaking changes through `0.x`.

## Installation

The development version from GitHub:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("viniciusoike/ggconsulting")
```

## Quick start

```{r example, fig.width = 7, fig.height = 4.5}
library(ggplot2)
library(ggconsulting)

ggplot(mtcars, aes(wt, mpg)) +
  geom_point() +
  labs(
    title    = "Fuel efficiency vs. vehicle weight",
    subtitle = "1974 Motor Trend data",
    caption  = "Source: datasets::mtcars"
  ) +
  theme_strategy()
```

`theme_strategy()` routes the palette's main colour through ggplot2 4.x's `from_theme()` mechanism, so unmapped geoms inherit it automatically — no `scale_color_*()` calls needed for the single-series case.

ggconsulting also sets a small set of aesthetic defaults on `library()` attach (currently `geom_point` `size = 2.5`). Opt out via:

```{r, eval = FALSE}
options(ggconsulting.autoload = FALSE)
# or, mid-session:
ct_unset_defaults()
```

## What's inside

**Themes**

- `ct_theme()` — composable theme builder with `palette`, `font`, `density`, and `context` arguments. Built on ggplot2 4.x `theme_sub_*()` helpers and routed through `element_geom()` for `from_theme()` linkage.
- `theme_strategy()` — minimal, generous-whitespace, navy-default preset inspired by top-tier global strategy consultancies.
- `theme_finance()` — serif preset with denser defaults (`density = "tight"`, `context = "report"`) tuned for printed pages and pitch books.
- `theme_editorial()` — serif preset with italic subtitles and a warmer palette for client memos and market commentary.

**Palettes and scales**

- Eleven shipped palettes — five strategy (`strategy_navy`, `strategy_emerald`, `strategy_crimson`, `strategy_azure`, `strategy_slate`), three finance (`finance_classic`, `finance_steel`, `finance_burgundy`), and three editorial (`editorial_warm`, `editorial_clay`, `editorial_oxide`).
- `scale_color_ct()` / `scale_fill_ct()` — discrete scales backed by the palettes; interpolate and warn when `n` exceeds the palette size.
- `scale_color_ct_c()` / `scale_fill_ct_c()` — continuous variants. British-spelling aliases (`scale_colour_ct*`) are also exported.
- `ct_palette_show()` — quick swatch preview for a single palette, a custom hex vector, or every shipped palette faceted.

**Locale-aware labels**

- `ct_locale("pt-BR" | "en-US")` — session-scoped locale switch stored in `options(ggconsulting.locale)`. Does not touch `Sys.setlocale()`; portable across Windows / Linux / macOS CI.
- `fmt_number()`, `fmt_pct()`, `fmt_delta()`, `fmt_currency()` — locale-aware formatters.
- `fmt_brl()` — always renders Brazilian Real with `R$` and a non-breaking space, regardless of active locale. Supports `style = "accounting"` for parens-wrapped negatives.
- `fmt_month()` — `Date` / `POSIXct` → localised month string, using internal pt-BR and en-US tables (no `LC_TIME` reliance).

**Data-aware polish layer**

- `ct_finish()` — runs *after* the geom layer is built and can inject value labels above bars or next to points, reorder a categorical x by y, format labels via shortcut names (`"brl"`, `"number"`, `"pct"`, `"delta"`) or a user-supplied function, highlight specific x values while muting the rest, label the last point of each line series, and apply geom-aware scale expansion.

**Mechanical wrappers**

- `ct_col()`, `ct_line()`, `ct_point()` — thin wrappers with consulting-grade defaults for call-site overrides.
- `ct_set_defaults()` / `ct_unset_defaults()` — `update_geom_defaults()`-driven aesthetic baseline with honest revert.

## Roadmap

`install_consulting_fonts()`, three vignettes (theme comparison, locale and number formatting, font setup), and a polished pkgdown gallery. The companion package `ctplot` — `ct_waterfall()`, `ct_slope()`, `ct_dumbbell()`, and PPT export via `officer` — will follow in a separate repo.
