---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 144
)
```

# ggconsulting

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/viniciusoike/ggconsulting/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/viniciusoike/ggconsulting/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/viniciusoike/ggconsulting/graph/badge.svg)](https://app.codecov.io/gh/viniciusoike/ggconsulting)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

An opinionated ggplot2 extension for executive-grade consulting output. Ships archetype themes, palettes, mechanical geom wrappers, and (in later releases) locale-aware label helpers and a data-aware polish layer.

> **Heads up:** ggconsulting is in early development. The public API is being shaped against real consulting decks; expect breaking changes through `0.x`.

## Installation

The development version from GitHub:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("viniciusoike/ggconsulting")
```

## Quick start

```{r example, fig.width = 7, fig.height = 4.5}
library(ggplot2)
library(ggconsulting)

ggplot(mtcars, aes(wt, mpg)) +
  geom_point() +
  labs(
    title    = "Fuel efficiency vs. vehicle weight",
    subtitle = "1974 Motor Trend data",
    caption  = "Source: datasets::mtcars"
  ) +
  theme_strategy()
```

`theme_strategy()` routes the palette's main colour through ggplot2 4.x's `from_theme()` mechanism, so unmapped geoms inherit it automatically — no `scale_color_*()` calls needed for the single-series case.

ggconsulting also sets a small set of aesthetic defaults on `library()` attach (currently `geom_point` `size = 2.5`). Opt out via:

```{r, eval = FALSE}
options(ggconsulting.autoload = FALSE)
# or, mid-session:
ct_unset_defaults()
```

## What's inside (v0.1 foundation)

- **`ct_theme()` / `theme_strategy()`** — composable theme builder and archetype preset. Built with ggplot2 4.x `theme_sub_*()` helpers and routed through `element_geom()` for `from_theme()` linkage.
- **Five starter palettes** — `strategy_navy`, `strategy_emerald`, `strategy_crimson`, `strategy_azure`, `strategy_slate`.
- **`ct_col()` / `ct_line()` / `ct_point()`** — mechanical wrappers with consulting-grade defaults for call-site overrides.
- **`ct_set_defaults()` / `ct_unset_defaults()`** — `update_geom_defaults()`-driven aesthetic baseline with honest revert.

## Roadmap

Next prompts will add `theme_finance()` / `theme_editorial()` archetypes, `scale_color_ct()` / `scale_fill_ct()`, `ct_finish()` polish layer, locale-aware label helpers (`fmt_brl`, `ct_locale`), `install_consulting_fonts()`, vignettes, and a polished gallery.
