---
title: "Themes and palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Themes and palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  fig.width = 7,
  fig.height = 4
)
```

```{r setup, message = FALSE}
library(ggplot2)
library(ggconsulting)
```

The package ships three theme presets — `theme_strategy()`, `theme_finance()`, and `theme_editorial()` — and colour scales backed by the built-in palettes. This article is a quick gallery: one small plot per theme, then the scales. All plots use the bundled datasets.

## Strategy

`theme_strategy()` is the minimal, whitespace-heavy preset with a navy palette by default.

```{r}
bu_last <- subset(bu_quarterly, quarter == max(quarter))

ggplot(
  bu_last,
  aes(reorder(business_unit, -revenue_brl), revenue_brl, fill = business_unit)
) +
  ct_col() +
  scale_fill_ct() +
  theme_strategy() +
  guides(fill = "none") +
  labs(x = NULL, y = "Revenue (R$ MM)")
```

## Finance

`theme_finance()` switches to serif type and denser defaults, tuned for reports.

```{r}
ggplot(client_nps, aes(quarter, nps, colour = segment)) +
  ct_line() +
  scale_color_ct("finance_classic") +
  theme_finance() +
  labs(colour = NULL, x = NULL, y = "NPS")
```

## Editorial

`theme_editorial()` uses serif type with a warmer palette, for analyst notes and commentary.

```{r}
ggplot(market_share, aes(year, share, fill = company)) +
  geom_area() +
  scale_fill_ct("editorial_warm") +
  scale_y_continuous(labels = fmt_pct(decimals = 0)) +
  theme_editorial() +
  labs(fill = NULL, x = NULL, y = "Market share")
```

## Scales and palettes

`scale_color_ct()` / `scale_fill_ct()` are discrete and map levels in palette order, interpolating with a warning past six levels. The `_c` variants are continuous and gradient across the palette. Any palette name — or any character vector of colours — pairs with any theme.

```{r}
ct_palette_show()
```

```{r}
ggplot(bu_quarterly, aes(quarter, business_unit, fill = headcount)) +
  geom_tile(linewidth = 0) +
  scale_fill_ct_c("editorial_oxide") +
  theme_editorial() +
  labs(x = NULL, y = NULL, fill = "Headcount")
```

See the reference pages for `reverse` (discrete) and `direction` (continuous).
